\textbf{Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)}

### 2024-01-21 manuscript_BiSC_outdoor_AP.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% --- Tittle of the paper --- %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\textbf{Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% --- Introduction --- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

Further details regarding the ADMS-Urban model and the variables used can be found in \textbf{Supplementary materials X}.

@@

We evaluated model performance using various statistical approaches and on different temporal resolutions. The LUR models were evaluated on an annual basis, DM were assessed both hourly and daily, and HM were evaluated on a weekly basis.

@@

\subsection{Dispersion model evaluation}
 Briefly, once the input data has been introduced to the ADMS Urban model, the calculation of NO\textsubscript{2}, PM\textsubscript{2.5}, and BC concentration levels has been carried out. Dispersion models were evaluated by comparing the yielded results from the ADM-Urban model with the real values measured by the air quality monitoring stations (XVPCA), including Ciutadella, Eixample, Gracia, Palau Reial, Poblenou, Sants, among others. The closer these values are, the better is the performance of the model.  Details from the metrics used for dispersion model validation and the XVPCA stations locations can be found in the \textbf{supplementary material}.\vspace{0.5cm}

\subsection{Hybrid model evaluation}
We assessed the performance of each hybrid model by contrasting predictions with observations. Two distinct validation approaches were employed: the \textit{10-fold cross-validation} and an external validation using 20\% of the data to test the performance of the model. While both methods vary in the sample size designated for training and testing, their core difference lies in the data-splitting strategy. In the 10-fold CV, the model trains on nine out of the ten data partitions and then validates against the remaining one, while in the external validation procedure the model uses all the data observations available to check the performance of the model.
We follow a grid search for hyperparameter tuning  to select the best configuration to obtain the optimal model based on the \textit{Root Mean Squared Error (R\textsuperscript{2})}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% --- Title of the paper --- %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\textbf{Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)}}

@@

\textbf{Keywords:} Air Pollution; Traffic-related air pollutants; Exposure assessment; Spatiotemporal models.

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% --- Introduction --- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

Further details regarding the ADMS-Urban model and the variables used can be found in \textbf{supplementary materials}.

@@

We evaluated model performance using various statistical approaches and on different temporal resolutions. The LUR models were evaluated on an annual basis, DM was assessed both hourly and daily, and HM was evaluated weekly.

@@

\subsection{Dispersion model evaluation}
 Briefly, once the input data has been introduced to the ADMS Urban model, the calculation of NO\textsubscript{2}, PM\textsubscript{2.5}, and BC concentration levels has been carried out. Dispersion models were evaluated by comparing the yielded results from the ADM-Urban model with the real values measured by the air quality monitoring stations (XVPCA), including Ciutadella, Eixample, Gracia, Palau Reial, Poblenou, Sants, among others. The closer these values are, the better the model's performance.  Details from the metrics used for dispersion model validation and the XVPCA stations locations can be found in the \textbf{supplementary material}.\vspace{0.5cm}

\subsection{Hybrid model evaluation}
We assessed the performance of each hybrid model by contrasting predictions with observations. Two distinct validation approaches were employed. Firstly,  
\textit{10-fold cross-validation} was used to provide an internal validation measure to this purpose the model was trained using 80\% of the data available. Secondly, external validation was performed by allocating 20\% of the data as a test set to further evaluate the model's performance. While both methods vary in the sample size designated for training and testing, their core difference lies in the data-splitting strategy. In the 10-fold CV, the model trains on nine out of the ten data partitions and then validates against the remaining one, while in the external validation procedure the model uses all the data observations available to check the performance of the model.
We follow a grid search for hyperparameter tuning  to select the best configuration to obtain the optimal model based on the \textit{Root Mean Squared Error (R\textsuperscript{2})}.
